\documentclass{book}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{physics}
\usepackage{tikz}
\usepackage[a4paper, margin=1in]{geometry}
\geometry{a4paper, margin=1in}
\usepackage{xcolor}
\graphicspath{ {./images/} }
\usepackage{svg}
\usepackage{bm}
\usepackage{appendix}
\renewcommand{\cleardoublepage}{\clearpage}
\tikzset{>=latex} % for LaTeX arrow head
\usepackage{xcolor}
{
\colorlet{veccol}{orange!90!black}
\colorlet{myblue}{blue!60!black}
\tikzstyle{vector}=[->,thick,veccol]
\def\R{1.4}
\def\r{0.03}
\def\N{9}
%\bm{\odot}%otimes
\def\RC{0.14}
\def\Cout{
  \tikz[baseline=-2.5]{ \draw[line width=0.7,myblue] (0,0) circle (\RC);
                        \fill[myblue] (0,0) circle (0.028); }
}
\def\Cin{
  \tikz[baseline=-2.5]{ \draw[line width=0.7,myblue] (0,0) circle (\RC)
                                                     (-135:0.75*\RC) -- (45:0.75*\RC)
                                                     (135:0.75*\RC) -- (-45:0.75*\RC); }
}
\def\null{\color{myblue}{0}}

}
\newtheorem*{theorem}{Theorem}
\title{Mathematics 2}
\author{Dominik Szablonski}

\begin{document}

\maketitle

\tableofcontents

\chapter{Partial Differentiation and Multiple Integration}
The differential function of a function $f = f(x,y)$ is given by,
\begin{equation}
    \dd{f} = \pdv{f}{x}\dd{x} + \pdv{f}{y}\dd{y}.
\end{equation}
\section{Taylor Series}
The Taylor series for a function $f(x_1,x_2,\ldots,x_m)$ about a point $(x_1^0,x_2^0,\ldots,x_m^0)$ is,
\begin{equation}
    f(x_1,x_2,\ldots,x_m) = f(x_1^0,x_2^0,\ldots,x_m^0) + \sum_{k=1}^{\infty}\frac{1}{k!}\left((x_1-x_1^0)\pdv[]{f}{x_1}+\cdots+(x_m + x_m^0)\pdv[]{f}{x_m}\right)^kf(x_1,x_2,\ldots,x_m),
\end{equation}
where the power on the bracket applies to the amount of times each differential is applied to $f$. Each partial derivative is evaluated about $(x_1^0,x_2^0,\ldots,x_m^0)$.
\section{Multiple Integration}
We are able to integrate over multiple variables. This allows for finding quantities such as a volume or area. 
\begin{equation}
    V = \int f(x,y,z)\dd{\tau} = \int \int \int f(x,y,z) \dd{x}\dd{y}\dd{z} = \int \left( \int \left( \int f(x,y,z) \dd{x}\right)\dd{y}\right)\dd{z}.
\end{equation}
\subsection{Areas and volumes in different coordinate systems}
\subsubsection{2D Plane Polar Coordinates}
\begin{align}
    x&=r\cos\theta & y&=r\sin\theta &\dd{A}&=r\dd{r}\dd{\theta}
\end{align}
\subsubsection{3D Cylindrical Polar Coordinates}
\begin{align}
    \text{Curved Surface: }\dd{A}&=r\dd{\theta}\dd{z} & \text{Top Surface: } \dd{A}&=r\dd{\theta}\dd{r} & \text{Volume: } \dd{V}=r\dd{r}\dd{\theta}\dd{z}
\end{align}
\subsubsection{3D Spherical Polar Coordinates}
\begin{align}
    \dd{A} &= r^2\sin\theta\dd{\theta}\dd{\phi} & \dd{V}&=r^2\sin\theta\dd{r}\dd{\theta}\dd{\phi}
\end{align}
There is an important identity required when working with polar co-ordinates,
\begin{equation}
    \sin\theta\dd{\theta} = -\dd{(\cos\theta)}.
\end{equation}
The limits for the volume of a sphere are,
\begin{equation}
    \int_0^{2\pi}\dd{\phi}\int_{0}^{\pi}\sin\theta\dd{\theta}\int_0^Rr^2\dd{r}.
\end{equation}
\subsection{Moment of Inertia}
The moment of inertia is given by,
\begin{equation}
    I = \int r_{\perp}^2\dd{m},
\end{equation}
which can be rewritten as,
\begin{equation}
    I = \rho\int r_{\perp}^2\dd{V},
\end{equation}
where $\rho$ is the density of the volume. For non-trivial axis, we use,
\begin{equation}
    r_{\perp} = |\vu{a}\cross\vb{p}|,
\end{equation}
where $\vu{a}$ is the vector in the direction of of the axis, and $\vb{p}$ is a generic vector such that,
\begin{equation}
    \vb{p} = r_i\vb{e}_i.
\end{equation}
\subsection{The Jacobian}
When converting between co-ordinate frames, we cannot always simply replace variables. We must use,
\begin{equation}
    \dd{x}\dd{y}\dd{z} = |J(u,v,w)|\dd{u}\dd{v}\dd{w}.
\end{equation}
Where, we can define,
\begin{align}
    x & = f(u,v,w) & y & = g(u,v,w) &z & = h(u,v,w) 
\end{align}
and then, the Jacobian is for a 2D system, the determinant of,
\begin{equation}
    \begin{vmatrix}
        \pdv{f}{u} & \pdv{f}{v} \\
        \pdv{g}{u} & \pdv{g}{v}
    \end{vmatrix}
\end{equation}
and for a 3D system,
\begin{equation}
    \begin{vmatrix}
         \pdv{f}{u} & \pdv{f}{v} & \pdv{f}{w} \\
        \pdv{g}{u} & \pdv{g}{v} & \pdv{g}{w} \\
        \pdv{h}{u} & \pdv{h}{v} & \pdv{h}{w}
    \end{vmatrix}.
\end{equation}
\chapter{Fields}
A field is an entity whose value depends on position. A field may be either \textbf{scalar} or \textbf{vector}. The direction of vector fields may also depend on position. \textbf{Scalar fields} are often represented by \textbf{contour lines}, which conenct the $x$ and $y$ points. \textbf{Vector fields} are often visualised using field lines. We can calculate the equations for these field lines by considering a vector field, $V = V_x \vu{i} + V_y\vu{j}$, and solving for,
\begin{equation}
    \dv{y}{x} = \frac{V_y}{V_x}.
\end{equation}
\section{Gradient $\grad$}
We can define the infinitesimal change in a scalar field as,
\begin{equation}
    d\psi = \grad \psi \cdot \dd{\vb{r}},
\end{equation}
where we define the \textbf{gradient} operator as,
\begin{equation}
    \grad = \pdv{}{r_i}\vb{e}_i.
\end{equation}
There are some properties of grad which we must be aware of. For a scalar field, $f(x,y,z)$,
\begin{itemize}
    \item $\grad f$ is a vector field.
    \item $\grad f$ represents the maximum rate of change of $f$.
    \item $\grad f$ is perpendicular to the contours of constant $f$.
    \item  The unit vector normal to a level surface is 
    \begin{equation}
        \frac{\grad f}{|\grad f|}.
    \end{equation}
\end{itemize}
There are two main types of questions where the grad operator is used,
\begin{enumerate}
    \item Finding the unit vector at $(x_0,y_0,z_0)$ which is normal to a level surface, $f(x,y,z)$.
    \begin{equation}
        \text{Obtain } \grad f(x,y,z) \to \vb{n} = \grad f(x_0,y_0,z_0) \to \vu{n} = \frac{\grad f(x_0,y_0,z_0)}{|\grad f(x_0,y_0,z_0)|}
    \end{equation}
    \item Find the rate of increase at $f(x_0,y_0,z_0)$ in the direction between, $(x_1,y_1,z_1)$ and $(x_2,y_2,z_2)$. 
    \begin{equation}
        \text{Eval. } \grad f(x_0,y_0,z_0) \to \dd{\vb{s}} = (\Delta x, \Delta y, \Delta z) \to \vu{u} = \frac{\dd{\vb{s}}}{|\dd{\vb{s}}|} \to \dv{f}{s} = \grad f(x_0,y_0,z_0) \cdot \vu{u}.
    \end{equation}
\end{enumerate}
where $\phi$ and $\psi$ are scalar fields and $K$ is a position independent constant scalar.
\subsection{Grad in polar coordinates}
\begin{align}
    \text{Cylindrical:} && \grad \psi & = \pdv{\psi}{r}\vu{r} + \frac{1}{r}\pdv{\psi}{\theta}\vu*{\theta} + \pdv{\psi}{z}\vu{z}, \\
    \text{Spherical:} && \grad \psi & = \pdv{\psi}{r}\vu{r} + \frac{1}{r}\pdv{\psi}{\theta}\vu*{\theta} + \frac{1}{r\sin \theta}\pdv{\psi}{\phi}\vu*{\psi}.
\end{align}
\section{Lagrangian Multipliers}
These are used when wanting to find the minimum or maximum of a field when a field $f$ is constrained by some function $g$. If $g$ is a constant constraint, then we can say that,
\begin{equation}
    \dd{g} = 0
\end{equation}
and for a minimum or maximum of $f$, similarly,
\begin{equation}
    \dd{f} = 0.
\end{equation}
We recall that the change in a scalar field along an elemental path is,
\begin{equation}
    \dd{\psi} = \grad \psi \cdot \dd{\vb{s}}.
\end{equation}
Thus, $\grad f$ and $\grad g$ are both perpendicular to $\dd{\vb{s}}$. Thus, $\grad f$ and $\grad g$ are parallel or anti parallel to each other. We can then state the relation,
\begin{equation}
    \grad f = \lambda \grad g
\end{equation}
which brings about a system of equations,
\begin{equation}
    \begin{split}
        \pdv{f}{x} - \lambda \pdv{g}{x} & = 0 \\
        \pdv{f}{y} - \lambda \pdv{g}{y} & = 0
    \end{split}
\end{equation}
We will want to include the function of $g$ when finding the solutions to this equation. 
\begin{enumerate}
    \item Find $x$,$y$, and $z$ in terms of $\lambda$.
    \item Substitute these into the expression for $g$.
    \item Substitute the value found for $g$ back into the expressions for $x$,$y$, and $z$ to find the coordinates of the maximum and minimum rate of change.
\end{enumerate}

\section{Div}
\begin{align}
    \text{Div}(\vb{F}) \equiv \div{\vb{F}}
\end{align}
The divergence describes the flux through an area of a  vector field. A field with 0 divergence is known as a \textit{solenoidal field} The total flux of a vector field through a volume composed of $i$ surfaces is given by the \textbf{divergence theorem},
\begin{equation}
\begin{split}
    \sum_i \int_{S_i}\vb{F}\cdot\dd{\vb{S}}_i = \int_V(\div{\vb{F}})\dd{V} \\
    \div{\vb{F}} = \frac{1}{|\vb{v}|}\int_S \vb{F}\cdot\dd{\vb{S}}
\end{split}
\end{equation}
Whether the flux is $+$ive, $-$ive or 0 will give us different information.\\\\
When $|\vb{F}| \equiv \text{const}$, we have,
\begin{equation}
    \div{\vb{F}} = 0.
\end{equation}
For \textit{increasing} $|\vb{F}|$, the total flux is given by,
\begin{equation}
    \int (F_R - F_L)\dd{s} 
\end{equation}
\begin{equation}
    F_R > F_L \therefore \div{\vb{F}} > 0 \implies \text{Net flow \textit{out of the volume.}}
\end{equation}
The field is known as a \textit{source} of flux.\\\\
For \textit{decreasing} $|\vb{F}|$,
\begin{equation}
    F_L > F_R \therefore \div{\vb{F}} < 0 \implies \text{Net flow \textit{into the volume.}}
\end{equation}
The field is then known as a sink of flux.
\\\\
For non-trivial fields, the values of Div still apply. 
\subsection{Div in polar coordinates}
For cylindrical polar coordinates,
\begin{equation}
    \div{\vb{A}} = \frac{1}{r}\pdv{}{r} \left(rA_r\right)+ \frac{1}{r}\pdv{}{\theta}A_{\theta} + \pdv{}{z}\left(A_z\right).
\end{equation}
For spherical polar coordiantes,
\begin{equation}
    \div{\vb{A}} = \frac{1}{r^2}\pdv{}{r}\left(r^2A_r\right) + \frac{1}{r\sin\theta}\pdv{}{\theta} \left(A_{\theta}\sin\theta\right) + \frac{1}{r\sin\theta}\pdv{}{\phi} \left(A_{\phi}\right)
\end{equation}
\subsection{Gauss' Law}
\begin{equation}
\begin{split}
    &\int\vb{E}\cdot\dd{\vb{S}} = \int_V(\div{\vb{E}})\dd{V} = \frac{1}{\epsilon_0}\int\dd{Q} \\
    &\div{\vb{E}} = \frac{1}{\epsilon_0}\dv{Q}{V} = \frac{\rho}{\epsilon_0}\\
\end{split}
\end{equation}
\section{Curl}
\begin{equation}
    \text{Curl}(\vb{F}) \equiv \curl{\vb{F}}
\end{equation}
We can interpret the physical nature of curl if we imagine dropped a ball into a field. If $(\curl{\vb{F}}) \neq 0$, then the ball will experience a torque. A field with 0 curl is known as an \textit{irrotational field}.
\subsubsection{Curl in polar coordinates}
For cylindrical polar coordinates,
\begin{equation}
    \curl{\vb{A}} = \frac{1}{r}\begin{vmatrix}
        \vu{r} & r\vu*{\theta} & \vu{k} \\
        \pdv{}{r} & \pdv{}{\theta} & \pdv{}{z} \\
        A_r & rA_{\theta} & A_z
    \end{vmatrix}
\end{equation}
For spherical polar coordinates,
\begin{equation}
    \curl{\vb{A}} = \frac{1}{r\sin\theta}\begin{vmatrix}
        \vu{r} & r\vu*{\theta} & r\sin\theta\vu*{\phi} \\
        \pdv{}{r} & \pdv{}{\theta} & \pdv{}{\phi} \\
        A_r & rA_{\theta} & r\sin\theta A_{\phi}
    \end{vmatrix}
\end{equation}

\section{The Laplacian Operator}
This is defined,
\begin{equation}
    \nabla^2 = \grad \cdot \grad.
\end{equation}
Such that,
\begin{equation}
    \nabla^2 = \sum_i \pdv[2]{}{r_i}.
\end{equation}
For a scalar field $\psi$, the Laplacian is,
\begin{equation}
    \nabla^2\psi = \sum_i\pdv[2]{\psi}{r_i}.
\end{equation}
For a vector field, $\vb{F}$, the Laplacian is given by,
\begin{equation}
    \nabla^2\vb{F} = \nabla^2A_i\vb{e}_i.
\end{equation}
\subsection{Laplacian in Polar Coordinates}
In cylindrical polar coordinates,
\begin{equation}
    \nabla^2\psi = \frac{1}{r}\pdv{}{r}\left(r\pdv{\psi}{r}\right) + \frac{1}{r^2}\pdv[2]{\psi}{\theta} + \pdv[2]{\psi}{z}.
\end{equation}
In spherical polar coordinates,
\begin{equation}
    \nabla^2\psi = \frac{1}{r^2}\pdv{}{r}\left(r^2\pdv{\psi}{r}\right) + \frac{1}{r^2\sin\theta}\pdv{}{\theta}\left(\sin\theta\pdv{\psi}{\theta}\right)+\frac{1}{r^2\sin\theta}\pdv[2]{\psi}{\phi}
\end{equation}

\section{Maxwell's Equations}
\begin{align}
    & \div{\vb{E}} = \frac{\rho}{\epsilon_0} & \text{Gauss' Law}&\\
    & \div{\vb{B}} = 0 & \text{No magnetic monopoles}&\\
    & \curl{\vb{E}} = -\pdv{\vb{B}}{t} & \text{Faraday's Law}&\\
    &\curl{\vb{B}} = \mu_0\vb{J} + \mu_0\epsilon_0\pdv{\vb{E}}{t} & \text{Ampere's Law}&
\end{align}
The wave equation for electromagnetic waves can then be derived,
\begin{equation}
    \nabla^2\vb{E} = \frac{1}{c^2}\pdv[2]{\vb{E}}{t}.
\end{equation}
\section{Helmholtz Decomposition}
If you have a smooth, rapidly varying field that vanishes faster than $\frac{1}{r}$ as $r \to \infty$,
\begin{equation}
    \vb{v} = \curl{\vb{\vb{A}}} + \grad\phi.
\end{equation}
We know that,
\begin{align}
    &\div{(\curl{\vb{A}})} = 0 & \curl{\grad\phi} = 0&\\
    &\text{"B-mode"} & \text{"E-Modes"}&
\end{align}

\section{Surface Integrals}
When we integrate over a surface, we usually integrate over a vector, given as,
\begin{equation}
    \dd{\vb{S}} = \vu{n}\dd{S}
\end{equation}
where $\vu{n}$ is a unit vector which is perpendicular and away from the surface. If our surface is described by a function $f$, we can compute $\vu{n}$ as,
\begin{equation}
    \vu{n} = \frac{\grad f}{\left|\grad f\right|}.
\end{equation}
The elemental area $\dd{S}$ can be rewritten in Cartesian coordinates if we consider that the elemental surface is inclined at some angle, $\theta$ to the $x-y$ plane. We then say,
\begin{equation}
    \begin{split}
        \dd{x}\dd{y} & = \dd{S}\cos\theta = \dd{S}(\vu{n}\cdot\vu{k}) \\
        & = \dd{\vb{S}}\cdot\vu{k}.
    \end{split}
\end{equation}
\subsection{Solid Angles}
We often wish to integrate over a solid angle. The infinitesimal element of a solid angle is given by,
\begin{equation}
    \dd{\Omega} = \sin\theta\dd{\theta}\dd{\phi}.
\end{equation}
Surface integrals over solid angles have the infinitesimal area element,
\begin{equation}
    \dd{\Omega} = \frac{\vu{r}\cdot\dd{\vb{S}}}{r^2}.
\end{equation}
\subsection{Flux}
The flux through of a vector field $\vb{A}$ through a surface $S$ is given by,
\begin{equation}
    \text{FLUX} = \int_S\vb{A}\cdot\dd{\vb{S}}.
\end{equation}
Often, it is a lot easier to do this using the Divergence theorem covered in the next section.
\section{Divergence Theorem}
\begin{theorem}
    The total flux of a vector $\vb{A}$ through a closed surface $S$ is related to the divergence of a vector field inside a volume $V$ by,
    \begin{equation}
        \int_S \vb{A}\cdot\dd{\vb{S}} = \int_V\div{\vb{A}}\dd{V}.
    \end{equation}
\end{theorem}\noindent 
This theorem can also be applied to scalar fields,
\begin{equation}
    \int_S \psi \dd{\vb{S}} = \int_V\grad\psi \dd{V}.
\end{equation}
\subsection{Applications of Divergence Theorem}
\subsubsection{Maxwell's First Equation}
Gauss' law can be given as follows,
\begin{equation}
	\int_S \vb{E}\cdot\dd{\vb{S}} = \frac{1}{\epsilon_0}\int_V \rho \dd{V}.
\end{equation}
Re-writing this in terms of the divergence theorem,
\begin{equation}
	\begin{split}
		\int_V \div{\vb{E}}\dd{V} &= \frame{1}{\epsilon_0}\int_V \rho \dd{V}\\
		\div{\vb{E}} & = \frac{\rho}{\epsilon_0},
	\end{split}
\end{equation}
which is Maxwell's first equationn of electromagnetism.
\subsubsection{The Continuity Equation}
This is a conservation equation, given by,
\begin{equation}
	\dv{\rho}{t} + \div{\vb{J}} = 0
\end{equation}
where $\rho$ is an amount of some quantity, $q$, per unit volume, and $\vb{J}$ is the flux per unit time of $q$.
\section{Line Integrals}
For a curve $C$ defined by a function $f$ and a small length element $\dd{l}$, the scalar line integral is defined by,
\begin{equation}
	\int_C f\dd{l}.
\end{equation}
For 2D line integrals, we can define,
\begin{equation}
	(\dd{l})^2 = (\dd{x})^2 + (\dd{y})^2
\end{equation}
and,
\begin{equation}
	l = \int_C \dd{l} = \int_{x_0}^{x_1} \sqrt{1 + \left(\dv{y}{x}\right)^2}\dd{x}.
\end{equation}
For a curve defined by parameters, i.e., $x = g(t)$, $y = h(t)$, we write,
\begin{equation}
	l = \int_{t_0}^{t_1}\sqrt{\left(\dv{x}{t}\right)^2 + \left(\dv{y}{t}\right)^2}\dd{x}.
\end{equation}
In polar co-ordinates,
\begin{equation}
	\dd{l} = \sqrt{r^2 + \left(\dv{r}{\theta}\right)^2}\dd{\theta}.
\end{equation}
\subsection{Vector line integrals}
For a vector $\vb{A}$, we define the samll length element vector as,
\begin{align}
	\dd{\vb{l}} = \dd{x}\vu{i} \dd{u}\vu{j} && \text{Cartesian} \\
	\dd{\vb{l}} = \dd{r}\vu{r} + r\dd{\theta}\vu*{\theta} && \text{Polar}.
\end{align}
The line integral is then given by,
\begin{equation}
	l = \int_C \vb{A} \cdot \dd{\vb{l}}.
\end{equation}
\subsection{Circulation of Vector Fields}
If we wish to find the circulation of a vector $\vb{A}$ along a certain path, $c$, we should compute $\vb{A}\cdot\dd{\vb{l}}$. If we define $c = c(x,y,z)$, then we should substitute appropriately so that we are able to integrate over $\vb{A}\cdot\dd{\vb{l}}$.
\\\\
To find the circulation over polar coordinates, we want to first parametrise the curve, such that,
\begin{align}
	x = g(\theta) && y = f(\theta)
\end{align}
and obtain a vector, $\vb{c}$,
\begin{equation}
	\vb{c} = (g(\theta),f(\theta)).
\end{equation}
We can then rewrite $\vb{A}$ in terms of the components of $\vb{c}$ and use,
\begin{equation}
	\vb{A}\cdot\dd{\vb{l}} = \vb{A}(\vb{c}) \cdot \dv{\vb{c}}{\theta}\dd{\theta}
\end{equation}
and perform the integral. For clockwise circulation this is $0 \to 2\pi$ and for anti-clockwise this is $2\pi \to 0$.
\subsection{Stoke's Theorem}
The circuation of a vector fied $\vb{B}$ is related to the surface integral of the curl by,
\begin{equation}
	\oint_C \vb{B}\cdot\dd{\vb{l}} = \int\int_S (\curl{\vb{B}})\cdot\dd{\vb{S}}
\end{equation}
We can use the right hand rule to determine the direction of $\dd{\vb{S}}$.
\section{Applications in electrcicity and magnetism}
\section{Applications in mechanics}
\chapter{Fourier series}
\appendix
\chapter{Vector Calculus Identities}
\section{Grad Identities}
\begin{align}
    & \grad(\psi + \phi) = \grad\psi + \grad\phi \\
    & \grad(K\psi) = K\grad\psi \\
    & \grad(\psi\phi) = \psi\grad\phi + \phi\grad\psi 
\end{align}
\section{Curl Identities}
\begin{align}
    & \curl{(\vb{A}+\vb{B})} = \curl{\vb{A}} + \curl{\vb{B}} \\
    & \curl{(\phi\vb{A})} = \phi(\curl{\vb{A}})+(\grad\phi)\cross\vb{A} \\
    & \curl{(\vb{A}\cross\vb{B})} = \vb{A}(\div{\vb{B}})-\vb{B}(\div{\vb{A}})+(\vb{B}\cdot\grad)\vb{A}-(\vb{A}\cdot\grad)\vb{B}
\end{align}
\section{Div Identities}
\begin{align}
    & \div{(\vb{A}+\vb{B})} = \div{\vb{A}} + \div{\vb{B}} \\
    & \div{(\phi\vb{A})} = (\grad\phi)\cdot\vb{A} +\phi(\div{\vb{A}}) \\
    & \div{(\vb{A}\cross\vb{B})} = \vb{B}\cdot(\curl{\vb{A}})-\vb{A}\cdot(\curl{\vb{B}})
\end{align}
\section{Combination Identities}
\begin{align}
    & \grad \cross \grad\phi = 0 \\
    & \grad \cdot (\curl{\vb{A}}) = 0 \\
    & \curl{(\curl{\vb{A}})} = \grad(\div{\vb{A}}) - \nabla^2\vb{A}.
\end{align}
\chapter{Vector Calculus Proofs}
\section{$\div{(g\vb{F})} = (\grad g)\cdot \vb{F} + g(\div{\vb{F}})$}
\begin{proof}
    \begin{equation*}
        \begin{split}
            \div{(g\vb{F})} & = (gF_1)_x + (gF_2)_y + (gF_3)_z \\
            & = g_xF_1 + g_y F_2 + g_z F_3 + g\left[(F_1)_x + (F_2)_y + (F_3)_z\right] \\
            & = \begin{pmatrix}
                g_x \\ g_y \\ g_z
            \end{pmatrix} \cdot \begin{pmatrix}
                F_1 \\ F_2 \\ F_3
            \end{pmatrix} + g\begin{pmatrix}
                (F_1)_x \\ (F_2)_y \\ (F_3)_z 
            \end{pmatrix}\\
            & = (\grad g)\cdot \vb{F} + g(\div{\vb{F}})
        \end{split}
    \end{equation*}
\end{proof}
\section{Ampere's Law}


\end{document}
